---
title: session3
author: CEU mentoring
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---



```{r, echo=FALSE, warning=F, message=F, warning=FALSE}
library(nycflights13)
library(tidyverse)
library(ggplot2)
df <- flights
# http://r-statistics.co/Top50-Ggplot2-Visualizations-MasterList-R-Code.html
# read about package nycflights13:
#  https://cran.r-project.org/web/packages/nycflights13/nycflights13.pdf
p1 <- 
mtcars %>% 
  ggplot(aes(x=mpg , y=hp)) + 
  geom_point()

# these two graphs are same, but option 1 uses pipes, which helps especially with lots of functions
p2 <-   ggplot(data = mtcars, aes(x=mpg , y=hp)) + 
  geom_point()
```


# Which airplane fought the most times?
```{r, echo=FALSE,message=F, warning=FALSE}
df %>%
  filter(!is.na(tailnum)) %>% # filter those without N/A
  group_by(tailnum) %>% 
  summarise('number_of_flights' = n() ) %>% # calculate the number of observations in each group
  arrange(-number_of_flights ) %>% # here using ".by_group = TRUE" or not doesn't make a difference, but it matters in other occasions!
  head(2)

# read mor about arrange() in the end
```

# Create the departure delay histogram
```{r, echo=FALSE, message=F, warning=FALSE}
df %>% 
ggplot(aes(x=dep_delay)) +
  geom_bar()+ 
  theme_bw()+
  labs(x='Departure delay', y='Number of observation', title = 'Departure delay histogram')

```


# Number of flights to destination
```{r, echo=FALSE, message=F, warning=FALSE}

df %>%
  group_by(dest)%>%
  # use summarize to calculate numbers, mean value...
  summarise('number_of_flights'=n()) %>%
  arrange(-number_of_flights) %>% 
  ggplot(aes(x=dest, y=number_of_flights) ) +
  geom_col()+
    labs(title='Number of flights to destination', y='Number of flights', x = 'Destination')



```

# Top 10 most popular destination

```{r, echo=FALSE, message=F, warning=FALSE}
df %>%
  group_by(dest)%>%
  summarise('number_of_flights'=n()) %>%
  arrange(-number_of_flights) %>% 
  head(10) %>% 
  # reorder(a,b) put a in b's order as desired
  ggplot(aes(x = reorder(dest, -number_of_flights), y = number_of_flights)) + 
  geom_col() +
  theme_classic()+
  labs(title='Top 10 most popular destination', y='Number of flights', x = 'Destination')

```

# The most exact destinations (dep_delay_is the least on average top 10)
```{r, echo=FALSE, message=F, warning=FALSE}

df %>%
  group_by(dest)%>%
  summarise('mean_delay'= mean(dep_delay, na.rm = T)) %>% #exclude N/A values
  arrange(mean_delay)%>%
  head(10)%>%
  ggplot(aes(x= reorder(dest, mean_delay), y = mean_delay)) + 
  geom_point(color='red') + 
  labs(title = 'The most exact destinations', x='Destination', y='Average late') + 
  theme_light()


```

# iris data plot
```{r, echo=FALSE}
iris %>%
  ggplot(aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point() +
  facet_wrap(~ Species)+
  theme_test()+
  labs( x='Length', y='Width')

```

PS: reading more about arrange()
arange() means arrange data in an customised order
```{r, echo=FALSE}
arrange(mtcars, cyl, disp) # first obey the sequence of cyl, then disp. The default is ascending.

# below two are basically the same, and option 1 is even better
arrange(mtcars, cyl, -disp) 
arrange(mtcars, cyl,desc(disp))
```

what's the difference among rank(), sort() and order()?

1. sort() sorts the vector in an ascending order.
2. rank() gives the respective rank of the numbers present in the vector; the default mode is descending (i.e. the largest number will get 1).
3. order() returns the indices of the vector in a sorted order.
```{r, include=TRUE}
print(sort(c (3, 1, 2, 5, 10))) # it manipulates numbers in the vector
print(rank(c (30, 1, 2, 5, 10))) # gives the rank of number in the vector # indexing
print(order(c (30, 1, 25, 50, 4))) # the second one should be in the first position, then the fifth one, then...
print(reorder(c (30, 1, 2, 5, 10),c(30, 1, 25, 50, 40)))
```

what's the difference between summarise() and mutate()?
1. mutate() adds a new column in the dataframe
2. summarise() create a new statistics in the memory.