---
title: R_practice_session-2
author: Deborah
date: Oct 8, 2020
output:
  rmarkdown::html_document:
    theme: lumen
---

## Create a folder somewhere and name it R_codes

setwd('/Users/wodediannao/Desktop/CodingInR')
dir.create('R_codes')

### Create a project name it mentoring_2, and select the R_codes folder to base folder

#created!


### Print out the workng directory
```{r }
getwd() 
#right answer
print(getwd())
```


### Download the AMZN data from ceulearning
### Save it into the working directory
### Read the data with fullpath and with relativ path
```{r }
da1 <- read.csv('~/Desktop/CodingInR/coding_practice/AMZN.csv') #full path
da2 <- read.csv('../../CodingInR/coding_practice/AMZN.csv') #relatie path
```


### How can you comment multiple lines?
```{r }
# print your answer 
# print your answer 
# print your answer 
# command + shift + c
print('command + shift + c')
```

### How can you add the pipe symbol?
```{r }
 #%>% command + shift + m
print('command + shift + m')
```

### How can you insert code block? Why is it good?
```{r }
# print your answer 
print(' ``` 
      ```')
# another answer
# code » insert chunk (shorcut not available)
```


### install a package called rtsdata, then run following lines
```{r }

install.packages('rtsdata')
update.packages('zoo')
install.packages('rtx')
library('rtsdata')
ticker <- 'TSLA'
start_date <- '2020-01-01'
end_date <- Sys.Date()
df <- data.frame(ds.getSymbol.yahoo(ticker, from = start_date, to = end_date))

```

### Rename the header, to open, high,low, close, volume, adjusted,

```{r }
colnames(df) <- c('open', 'high','low', 'close', 'volume', 'adjusted')
```


### Create a column which contains the dates value
```{r }
df$dates <- c(row.names(df)) #amazing!
```


### Delete the adjusted column
```{r }
df <- df[-6]
#answer answer
df$adjusted <- NULL
```

### Create a column which indicate that if the close price is above the mean of close price use if-else
```{r }
library('dplyr')
mutate(df, above_mean = ifelse(close > mean(close), 'above', 'below'))

```

### Create a column with the year value it should be string
```{r }
df$year = substr(df$dates, 1,4)
```

### Save the clean data into xlsx, csv, rds format, save table it with '#'separator as .txt 
```{r }
write.csv(df, "amazon.csv")
write.table(df, 'amazon_t.txt', sep = '/#')

install.packages("writexl")
library('writexl')
write_xlsx(df, "amazon_x.xlsx")

saveRDS(df, "amazon_rds.rds")
```

### Change the theme of rmd with preaty doc

