---
title: "Explore2_8"
author: "Flamingo"
date: "1/14/2021"
output: html_document
---
* some preparatory work
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# so we can install packages in one line
library(nycflights13) # but not to call them in one line
library(gapminder)
library(Lahman)
library(ggplot2) # it has mpg dataframe
library(tidyverse)
```

3.2.4 Exercises
3.2.4.1 Run ggplot(data = mpg). What do you see?
-- nothing as x and y are not indicated
```{r}
ggplot(data = mpg)
```

3.2.4.2 How many rows are in mpg? How many columns?
-- 234 and 11
```{r}
nrow(mpg)
ncol(mpg)
```

3.2.4.3 What does the drv variable describe? Read the help for? mpg to find out.
-- the type of drive train, where f = front-wheel drive, r = rear wheel drive, 4 = 4wd

3.2.4.4 Make a scatterplot of hwy vs cyl.
```{r}
mpg %>% 
  ggplot(aes(x= hwy, y = cyl)) +
  geom_point()
```

3.2.4.5 What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
--  The resulting scatterplot has only a few points.
```{r}
mpg %>% 
  ggplot(aes(x= class, y = drv)) +
  geom_point()
```

An aesthetic is a visual property of the objects in your plot. Aesthetics include things like the size, the shape(0-20), or the color (they are called "levels") of your points. 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = manufacturer))
```

3.3.1 Exercises
What’s gone wrong with this code? Why are the points not blue?
-- "color" should be outside of aes and inside grom_point
-- within aes you will get the third category
```{r}
# the wrong codes:
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy),  color = "blue")
```

Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?
-- categorical: manufacturer, model, trans, drv, fl, class
-- continuous: cyl, displ, year, hwy, cty
-- use brains and check the type of each variable: Those with <chr> above their columns are categorical, while those with <dbl> or <int> are continuous.

Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?
-- color works for both
-- size for discrete
-- shape for categorical
```{r}
# color: continuous vs. discrete
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cyl))

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = manufacturer))
# shape: not work for continuous variable
# ggplot(data = mpg) + 
#   geom_point(mapping = aes(x = displ, y = hwy, shape = cyl))
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, shape = manufacturer))

# size:
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, size = cyl))

ggplot(data = mpg) + # works, but looks like a disaster and not make sense
  geom_point(mapping = aes(x = displ, y = hwy, size = manufacturer))
```

What happens if you map the same variable to multiple aesthetics?
-- it works even though a bad one. Avoid mapping a single variable to multiple aesthetics as it's redundant work.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = cyl, size = cyl))
```

What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)
-- Stroke changes the size of the border for shapes (21-25). These are filled shapes in which the color and size of the border can differ from that of the filled interior of the shape.
```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, colour = "black", fill = "white", size = 5, stroke = 5)
```

What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.
-- Yeah it also works
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5))
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2) 

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(drv ~ cyl)
```
3.5.1 Exercises
What happens if you facet on a continuous variable?
-- The continuous variable is converted to a categorical variable, and the plot contains a facet for each distinct value.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ year, nrow = 2) 
```

What do the empty cells in plot with facet_grid(drv ~ cyl) mean? How do they relate to this plot?
-- The empty cells (facets) in this plot are combinations of drv and cyl that have no observations. 
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = drv, y = cyl)) +
  facet_grid(drv ~ cyl)
```
What plots does the following code make? What does . do?
-- The symbol '.' ignores that dimension when faceting. For example, 'drv ~ .' facet by values of drv on the y-axis.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```
-- The symbol . ignores that dimension when faceting. For example, drv ~ . facet by values of drv on the y-axis.
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

Take the first faceted plot in this section:
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_wrap(~class, nrow = 2)

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```
What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger data set?
-- advantage: the ability to encode more distinct categories.
-- disadvantage: difficulty of comparing the values of observations between categories since the observations for each category are on different plots.

Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?
-- The arguments nrow (ncol) determines the number of rows (columns) to use when laying out the facets. It is necessary since facet_wrap() only facets on one variable.
-- The nrow and ncol arguments are unnecessary for facet_grid() since the number of unique values of the variables specified in the function determines the number of rows and columns.

When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
-- There will be more space for columns if the plot is laid out horizontally (landscape).

geom: geometrical object that a plot uses to represent the data.
Not all geom_ function can accept same aes settings, e.g. you can't set the "shape" of a line but rather chang the line type:
```{r}
ggplot(data = mpg) + 
  geom_smooth(aes(x = displ, y = hwy, linetype = drv))
```

use group aesthetic to a categorical variable to draw multiple objects:
```{r}
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
              
ggplot(data = mpg) +
  geom_smooth(mapping = aes(x = displ, y = hwy, group = drv))
    
ggplot(data = mpg) +
  geom_smooth(
    mapping = aes(x = displ, y = hwy, color = drv),
    show.legend = FALSE # no need to display legend
  )

mpg %>% group_by(drv) %>% # we use group_by() function but it didn't work
  ggplot() +
  geom_smooth(mapping = aes(x = displ, y = hwy))
```

change the variables in multiple geoms to a global level:
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()
```

set global and local varibles at different levels:
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth()
```

geom_line just displays a subset of mpg data set, which overrides the global data in ggplot() for this layer only.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(data = filter(mpg, class == "subcompact"), se = FALSE)
```

3.6.1 Exercises

Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + #global setting
  geom_point() + 
  geom_smooth(se = FALSE)
```

Will these two graphs look different? Why/why not? same
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

Recreate the R code necessary to generate the following graphs.
```{r}
mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point() +
  geom_smooth()

mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point() +
  geom_smooth(aes(group = drv))

mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point(aes(color = drv)) +
  geom_smooth()

mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point() +
  geom_smooth()

mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point(aes(color = drv)) +
  geom_smooth(aes(linetype = drv))

mpg %>% 
  ggplot(aes(y= hwy, x= displ)) +
  geom_point(size = 4, colour = "white") +
  geom_point(aes(colour = drv )) #two grpahs overlapping each other

```

use a stat (transformed variable):
```{r}
demo <- tribble(
  ~cut,         ~freq,
  "Fair",       1610,
  "Good",       4906,
  "Very Good",  12082,
  "Premium",    13791,
  "Ideal",      21551
)

ggplot(data = demo) +
  geom_bar(mapping = aes(x = cut, y = freq), stat = "identity")

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = stat(prop), group = 1))

ggplot(data = diamonds) + 
  stat_summary(
    mapping = aes(x = cut, y = depth),
    fun.min = min,
    fun.max = max,
    fun = median
  )
```

3.7.1 Exercises
What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
-- geom_pointrange()
--  The default stat for geom_pointrange() is identity() but we can add the argument stat = "summary" to use stat_summary() instead of stat_identity(), as belows:
```{r}
ggplot(data = diamonds) +
  geom_pointrange(
    mapping = aes(x = cut, y = depth),
    stat = "summary",
    fun.min = min,
    fun.max = max,
    fun = median
  )
```

What does geom_col() do? How is it different to geom_bar()?
-- The geom_col() function has different default stat than geom_bar(). The default stat of geom_col() is stat_identity(), which leaves the data as is. The geom_col() function expects that the data contains x values and y values which represent the bar height.

-- The default stat of geom_bar() is stat_count(). The geom_bar() function only expects an x variable. The stat, stat_count(), preprocesses input data by counting the number of observations for each value of x. The y aesthetic uses the values of these counts.

What variables does stat_smooth() compute? What parameters control its behaviour?
* y: predicted value
* ymin: lower value of the confidence interval
* ymax: upper value of the confidence interval
* se: standard error
* method, formula...

In our proportion bar chart, we need to set group = 1. Why? In other words what is the problem with these two graphs?
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = after_stat(prop)
                         ))

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = color, y = ..count.. / sum(..count..)))
```
colour a bar chart using "fill":
```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, colour = cut))

ggplot(data = diamonds, aes(fill = cut)) + 
  # put "fill = cut" in either ggplot(aes()) or geom_bar(aes())
  geom_bar(mapping = aes(x = cut))

ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity))
```

position = identity/fill/dodge/jitter:
```{r}
ggplot(data = diamonds, mapping = aes(x = cut, fill = clarity)) + 
  geom_bar(alpha = 1/5, position = "identity")
ggplot(data = diamonds, mapping = aes(x = cut, colour = clarity)) + 
  geom_bar(fill = NA, position = "identity")

ggplot(data = diamonds) + # easy to compare proportions across groups
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "fill") 

ggplot(data = diamonds) + 
  # makes it easier to compare individual values (which is largest in each group)
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge")

ggplot(data = mpg) + # overplotting
  geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```

3.8.1 Exercises
What is the problem with this plot? How could you improve it?
* There is overplotting because there are multiple observations for each combination of cty and hwy values. Jittering helps show the locations where there are more observations.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()

# corrected version
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point(position = "jitter")
```

* What parameters to geom_jitter() control the amount of jittering?
  * width and height
  
Compare and contrast geom_jitter() with geom_count().

* count(): Combinations of (x, y) values with more observations will be larger than those with fewer observations.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_jitter()

ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_count() 

```

What's the default position adjustment for geom_boxplot()? Create a visualization of the mpg data set that demonstrates it.
* The default position for geom_boxplot() is "dodge2", which is a shortcut for position_dodge2. This position adjustment does not change the vertical position of a geom but moves the geom horizontally to avoid overlapping other geoms.
```{r}
ggplot(data = mpg, aes(x = drv, y = hwy, colour = class)) +
  geom_boxplot() # can be one continuous & one discreet or one continuous alone
```

coord_flip() switches the x and y axes:
```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot()
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot() +
  coord_flip()
```

coord_quickmap() sets the aspect ratio correctly for maps:
```{r}
nz <- map_data("nz")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "grey")

ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_quickmap()
```

coord_polar() uses polar coordinates, which reveal an interesting connection between a bar chart and a Coxcomb chart.
```{r}
bar <- ggplot(data = diamonds) + 
  geom_bar(aes(x = cut, fill = cut), show.legend = FALSE) + 
  theme(aspect.ratio = 1) +
  labs(x = NULL, y = NULL)

bar
bar + coord_flip() # aha real bar chart!
bar + coord_polar()
```

Exercise 3.9.1
Turn a stacked bar chart into a pie chart using coord_polar().
```{r}
ggplot(mpg, aes( x = c(1), fill = drv)) + # can be c(a) or facor(1)
  geom_bar()

ggplot(mpg, aes( x = c(1), fill = drv)) +
  geom_bar() +
  coord_polar(theta = "y") # variable to map angle to (x or y), the most crucial step
```

What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
* The function coord_fixed() ensures that the line produced by geom_abline() is at a 45-degree angle. A 45-degree line makes it easy to compare the highway and city mileage to the case in which city and highway MPG were equal.
```{r}
p <- ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  geom_abline() # add a diagnoal reference line
p
p + coord_fixed()
```

code template:
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(
     mapping = aes(<MAPPINGS>),
     stat = <STAT>, 
     position = <POSITION>
  ) +
  <COORDINATE_FUNCTION> +
  <FACET_FUNCTION>









