---
title: session2
author: your name
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

### Create a folder somewhere and name it R_codes
### Create a project name it mentoring_2, and select the R_codes folder to base folder

### Print out the workng directory
```{r }
library(prettydoc)
print(getwd())
# you can change it with setwd() 
```


### Download the AMZN data from ceulearning
### Save it into the working directory
### Read the data with fullpath and with relativ path
```{r }
# if you created a working directory, file name is enough
# write '' and press tab it will list out the current filepath
df <- read.csv(file = 'AMZN.csv')

#full path 
df<- read.csv('/home/mihaly/R_codes/R_mentoring/AMZN.csv')
# if you are in mac startswith '/Users/'
# on windows 'C:/' and always press tab
 



```


### How can you comment multiple lines?
```{r }
# print your answer 
# it is also uncomment the selected rows
print('ctrl + shift+ c')
```

### How can you add the pipe symbol?
```{r }
# print your answer 
print('ctrl + shift + m')
```

### How can you insert code block? Why is it good?
```{r }
# print your answer 
print('code -> insert chunk')
```


### Install a package called rtsdata



```{r }
#install.packages('rtsdata') 
library(rtsdata)
ticker <- 'TSLA'
start_date <- '2020-01-01'
end_date <- Sys.Date()
df <- data.frame(ds.getSymbol.yahoo(ticker, from = start_date, to = end_date))

```

### Rename the header, to open, high,low, close, volume, adjusted,

```{r }
#it is a vector
print(names(df))
# you can change element one by one
print(names(df)[1])
names(df)[1] <- 'open'

# but you can change also in one line
names(df) <- c('open', 'high', 'low', 'close', 'volume', 'adjusted')




```


### Create a column which contains the dates value
```{r }
# the date values are in row.names 
# print the first ten
print(row.names(df)[1:10])
print(head(row.names(df), n = 10))

# createing a new column is simple just use dataframe name and $ and what you write after that will be the name of new column
df$date <- row.names(df)
# you can also create a new colmn in this way
df[['date']] <-  row.names(df)

#  [['column_name']] is same as $column_name

```


### Delete the adjusted column
```{r }
# just send back null to any vector
df$adjusted <- NULL
```

### Create a column which indicate that is the close price is above the mean of close price use ifelse
```{r }
#this is a vector
ifelse(df$close > mean(df$close), 'it is above', 'it is below')
# you can assign into a column
df$above_mean <- ifelse(df$close > mean(df$close), 'it is above', 'it is below')
```

### Create a column with the year value it should be string
```{r }
df$year <- substring(df$date, 1, 4  )


```

### Save the clean data into xlsx, csv, rds format, save table it with '#'separator as .txt 
```{r }
#install.packages("writexl")
library(writexl)
writexl::write_xlsx(df,'tsla_data.xlsx')
write.csv(df, 'tsla_data.csv') 
write.csv(df, 'tsla_data_without_rownames.csv', row.names =F ) # if you do not want to ad row.names
saveRDS(df, 'tsla_data.rds')
write.table(df, 'tlsa_data_with_hashtag.txt', sep = '#')



```

### Change the theme of rmd with preaty doc
# https://prettydoc.statr.me/index.html
