---
title: 'session 6'
author: CEU mentoring
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---



Exercise 1
Write a function that calculates number a to the power of b, but let b have a default value of 2.


```{r, echo=FALSE}
library(ggplot2)
library(prettydoc)
# https://www.r-exercises.com/2018/04/27/well-behaved-functions-exercises/

# Solutions
# https://www.r-exercises.com/2018/04/27/well-behaved-functions-solutions/




```

Exercise 2
Write a function that changes the value of pi in the R global environment to whatever you specify as the argument. Note: it is not recommended to re-define the value of “pi” in a real-life R program.

Example

pi

[1] 3.141593

chpi(4)

pi

[1] 4

chpi("I like cats")

pi

[1] "I like cats"



Exercise 3 
Create a function which return a data frame like the example.
The input of the function will be the number of rows of the data frame

```{r, echo=FALSE}
random_df  <- function(number_of_rows=10) {
  
  weight <- sample(50:95, number_of_rows, replace = T)
  height <- sample(150:210, number_of_rows, replace = T)
  t_class <- sample(c('A', 'B', 'C', 'D'), number_of_rows, replace = T)
  birth_date <- sample(seq(as.Date('1990-01-01'), as.Date('2000-01-01'), 'days'), number_of_rows, replace = T)
  tdf <- data.frame('weight'= weight, 'height' = height, 'class' = t_class, 'birth_date'= birth_date )
  tdf$age_days <- as.numeric(Sys.Date() - tdf$birth_date)
  tdf$age_year <- round(tdf$age_days/365, 1)
  return(tdf)
  
}


```


```{r}
print(random_df(15))

```

Exercise 4 
Create a function which print a random walk just like in previous class and return with the dataframe.


```{r, echo=FALSE}
get_random_walk  <- function(forward_length, backward_length, distance) {
  all_steps <- NULL
while (TRUE) {
  t_step <- sample(c(forward_length, (backward_length* -1) ), 1)
  all_steps <- c(all_steps, t_step)
  t_progress<- tail(cumsum(all_steps), 1)
  if (t_progress >=distance) {
    print(paste0('I need ', length(all_steps), ' steps to get home.'))
    break()
  }  
}

df <- data.frame('steps'= 1:length(all_steps), 'progress'= cumsum(all_steps) )

plot(ggplot(df, aes(x=steps, y=progress))+
  geom_line()+
  theme_bw()
)
return(df)
}  


```



```{r}
get_random_walk(forward_length = 1, backward_length = 0.9, distance = 100)
```

```{r}
head(df)
```

Go to [this site](https://www.r-exercises.com/2017/04/20/user-defined-functions-in-r-part-1/) and solve the tasks







