---
title: 'session 5'
author: CEU mentoring
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---



Exercise 1
Write a for loop that iterates over the numbers 1 to 7 and prints the cube of each number using print().

```{r, echo=FALSE}
library(ggplot2)
library(prettydoc)
# https://www.r-exercises.com/2018/03/30/loops-in-r-exercises/
for (i in 1:7) {
  print(i^3)
}

```
Exercise 2
Write a for loop that iterates over the column names of the inbuilt iris dataset and print each together with the number of characters in the column name in parenthesis. Example output: Sepal.Length (12). Use the following functions print(), paste0() and nchar().

```{r, echo=FALSE}
for (i in names(iris)) {
  print(paste0(i, ' (', nchar(i), ')' ) )
}

```


Exercise 3

Write a while loop that prints out standard random normal numbers (use rnorm()) but stops (breaks) if you get a number bigger than 1.

```{r, echo=FALSE}
while (TRUE ) {
  t <- rnorm(1)
  if (t>1) {
    print(paste0(t, ' is bigger than 1 the loop stopped'))
    break() 
  }else{
    print(t)
  }
}


```


Exercise 4

Using next adapt the loop from last exercise so that doesn’t print negative numbers.

```{r, echo=FALSE}
while (TRUE ) {
  t <- rnorm(1)
  if (t<0) {
    next()
  }
  if (t>1) {
    print(paste0(t, ' is bigger than 1 the loop stopped'))
    break() 
  }else{
    print(t)
  }
}


```

Exercise 5

Using a for loop simulate the flip a coin twenty times, keeping track of the individual outcomes (1 = heads, 0 = tails) in a vector that you preallocte.

```{r, echo=FALSE}
flips<- NULL
for (i in 1:20) {
  flips <-c( flips, sample(c(0,1), 1) )
}
print(flips)

#sample(c(0, 1), 20, replace = T)

```

Exercise 6

Use a while loop to investigate the number of terms required before the product

1⋅2⋅3⋅4⋅…

reaches above 10 million.

```{r, echo=FALSE}
all_product <- 1
t_number <- 1
while (TRUE) {
  print(t_number)

  all_product <- all_product*t_number
  if (all_product>10000000) {
    print(paste0('The solution is: ', t_number, ' the product is: ',all_product ))
    break()
  }
    t_number <-t_number +1
  
  
}


```


Exercise 7

Drunk people theory.

You need to go home which is 1500m far from you right now.

In one step you can go 1m closer or 0.9m back (you are drunk)

How many steps you need to reach home?

Plot your result. 

Simulate it 10 times


```{r, echo=FALSE}

for (i in 1:5) {
  


all_steps <- NULL
while (TRUE) {
  t_step <- sample(c(1, -0.9), 1)
  all_steps <- c(all_steps, t_step)
  t_progress<- tail(cumsum(all_steps), 1)
  if (t_progress >=1500) {
    print(paste0('I need ', length(all_steps), ' steps to get home.'))
    break()
  }  
}

df <- data.frame('steps'= 1:length(all_steps), 'progress'= cumsum(all_steps) )

plot(ggplot(df, aes(x=steps, y=progress))+
  geom_line()+
  theme_bw()
)
}

```

Exercise 8

Implement a multiplication game. A while loop that gives the user two random numbers from 2 to 12 and asks the user to multiply them. Only exit the loop after five correct answers. Try using as.integer(readline()) instead of scan() this time.

Exercise 9 

Make a lotery simulation.
Ask 5 number from the user and simulate the lottery draw from 90 ball, and write the result back to the user. 





