---
title: 'Data wrangling : Cleansing – Regular expressions'
author: "Jia-li"
date: "12/4/2020"
output: html_document
---
run the following commands to create the strings that we will work on.
```{r }
textmeta <- "R|is|cool,|so|are|you|that|you|are|for|__|your|skills|by|solving|this|exercise. Moreover parenthesis symbol is []! Finally once you are done with this set go for a coffee, you deserve it!"

textseq <- "I hope you are using R version 3.4.0 and you have updated on 2017-04-21, with nickname:'You stupid Darkness'."
```

Exercise 1

From object textmeta substitute the full stop (‘.’) with exclamation mark (‘!’) and assign the result to the object text.

```{r}
gsub('.','!', textmeta)
```

Exercise 2

From object text substitute the double underscore (‘__’) with ‘enhancing’ and assign the result to the object text.
```{r}
textmeta <- gsub('__','enhancing', textmeta)
```

Exercise 3

From object text substitute the backslash (‘\’) with a letter-spacing (‘ ‘) and assign the result to the object text.
