---
title: "Dplyr Basic Functions – Exercises"
author: "Flamingo"
date: "1/14/2021"
output: html_document
---
This file contains what I read from [Yihui Xie's blog]("https://yihui.org/knitr/options/") and also r exercise solutions regarding data wrangling.

1. We can choose which which r expression(s) to echo in a chunk, such as echo = 2:3 or echo = -4.
2. This "r setup" part is a global chunk option.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```
Exercise 1

Select the first three columns of the iris dataset using their column names. HINT: Use select().
```{r}
head(iris)
iris %>% 
  select(Sepal.Length, Sepal.Width,Petal.Length)
```

Exercise 2

Select all the columns of the iris dataset except “Petal Width”. HINT: Use “-“.
```{r}
iris %>% 
  select(-Petal.Width)
```

Exercise 3

Select all columns of the iris dataset that start with the character string “P”.
```{r}
iris %>% 
  select(starts_with('p'))
```

Exercise 4

Filter the rows of the iris dataset for Sepal.Length >= 4.6 and Petal.Width >= 0.5.
```{r}
iris %>% 
  filter(Sepal.Length >= 4.6, Petal.Width >= 0.5)
```

Exercise 5

Pipe the iris data frame to the function that will select two columns (Sepal.Width and Sepal.Length). HINT: Use pipe operator.
```{r}
iris %>% 
  select(Sepal.Width , Sepal.Length)
```

Exercise 6

Arrange rows by a particular column, such as the Sepal.Width. HINT: Use arrange().
```{r}
iris %>% 
  arrange(-Sepal.Width)
```

Exercise 7

Select three columns from iris, arrange the rows by Sepal.Length, then arrange the rows by Sepal.Width.
```{r}
iris %>% 
  select(Sepal.Length, Sepal.Width, Petal.Length) %>% 
  arrange(Sepal.Length, Sepal.Width) 
```

Exercise 8

Create a new column called proportion, which is the ratio of Sepal.Length to Sepal.Width. HINT: Use mutate().
```{r}
iris %>% 
  mutate(proportion = Sepal.Length / Sepal.Width)
```

Exercise 9

Compute the average number of Sepal.Length, apply the mean() function to the column Sepal.Length, and call the summary value “avg_slength”. HINT: Use summarize().
```{r}
iris %>% 
  summarise(avg_slength = mean(Sepal.Length))
```

Exercise 10

Split the iris data frame by the Sepal.Length, Compute the average number, minimum number and maximum number of Sepal.Length. HINT: Use group_by().
```{r}
iris %>% 
  group_by(Sepal.Length) %>% 
  summarise(avg_slength = mean(Sepal.Length),
            min_slength = min(Sepal.Length),
            max_slength = max(Sepal.Length),
            total = n()) #n() gives the current group size.
```
