---
title: "rmd_exercise"
author: "Deborah"
date: "12/3/2020"
output: html_document
---
Exercise 3 Display the summary of “cars” dataset in your report. HINT: Use summary().

```{r}
summary(cars)
```

Exercise 4

Make a plot of the “cars” dataset under the summary you just created. HINT: Use plot().

You can also embed plots, for example:

```{r} 
plot(cars) # default of echo is true
```
Exercise 5

Create a small experimental dataframe and dipslay it in your report. HINT: Use data.frame().
```{r}
L3 <- LETTERS[1:3]
fac <- sample(L3, 10, replace = TRUE)
d <- data.frame(x = 1, y = 1:10, fac = fac)
d # no need to add "print()"
```
Exercise 7

Load the package “knitr” in your .Rmd file. and hide the code chunk. HINT: Use echo.
```{r,echo= F}
library(knitr)
```
Exercise 9

Set fig.width and fig.height of your plot to 5.
```{r, fig.width=5, fig.height=5}
plot(cars)
```

Exercise 10

Change the file format of your plot from .png to .svg. HINT: Use dev.
```{r,fig.width=5, fig.height=5, echo=FALSE,,dev= svg}
plot(cars)
```

Exercise 1

Make a table out of the object dataframe you created and set its numbers to have one significant figure. HINT: Use kable().
```{r, knitr}
kable(d, digits = 1)
```

Exercise 6

Create manually a small table for your dataframe.
```{r, knitr, echoo =  false, warning=false}
A <- c("Bob", "Tom", "Bill", "Joe")
kable(dataframe, digits = 1)
```

Exercise 7

Apply right alignment to the column “B”. # by default it's already alightment to B column


Exercise 8

Create an unordered list of the contents of column “A” of your dataframe. # copy and past

Exercise 9

Transform the list you just created to ordered. # copy and past









