---
title: Nineteen Years Later
author: Harry Potter
date: July 31, 2016
output:
  rmarkdown::html_document:
    theme: lumen
---

### Create a folder somewhere and name it R_codes
### Create a project name it mentoring_2, and select the R_codes folder to base folder

### Print out the workng directory
```{r }
library(prettydoc)
```


### Download the AMZN data from ceulearning
### Save it into the working directory
### Read the data with fullpath and with relativ path
```{r }
data_in <- "~/Desktop/ECBS-5208-Coding-1-Business-Analytics/coding_practice"
AM <- read.csv(paste0(data_in,'/AMZN.csv'))


```


### How can you comment multiple lines?
```{r }
print('Ctrl+Shift+C')  
```

### How can you add the pipe symbol?
```{r }
# print your answer
print('conmand + shift + m') 
```

### How can you insert code block? Why is it good?
```{r }
# print your answer 
print('')
```


### install a package called rtsdata

```{r }

library(rtsdata)
ticker <- 'TSLA'
start_date <- '2020-01-01'
end_date <- Sys.Date()
df <- data.frame(ds.getSymbol.yahoo(ticker, from = start_date, to = end_date))

```

### Rename the header, to open, high,low, close, volume, adjusted,

```{r }
names (df)[1] <- "open"
names (df)[2] <- "high"
names (df)[3] <- "low"
names (df)[4] <- "close"
names (df)[5] <- "volume"
names (df)[6] <- "adjusted"

```

### Create a column which contains the dates value
```{r }
df$dates <- c("yy-mm-dd")
df$dates <- rownames(df)
df$dates  <- df$open
str(1:nrow(df)) # ???
```


### Delete the adjusted column
```{r }
df$adjusted <- NULL # right
```

### Create a column which indicate that the close price is above the mean of close price use ifelse
```{r }
df$CloseValueAboveMean <- ifelse(df$close > mean(df$close), yes = "True", no = "False")
```

### Create a column with the year value it should be string
```{r }
df$Year <- substring(df$dates, 1, 4)
```


### Save the clean data into xlsx, csv, rds format, save table it with '#'separator as .txt 
```{r }
write.csv(df, 'tsla.csv', row.names = FALSE)

write.table(is.data.frame(df))

saveRDS(df, "amazom.rds")

library('writexl')
write_xlsx(df, "amazon_x.xlsx")
```

### Change the theme of rmd with preaty doc
library(prettydoc)

