---
title: "workflow"
author: "Flamingo"
date: "1/16/2021"
output: html_document
--- 
Tibbles are data frames, but slightly tweaked to work better in the tidyverse. 
```{r}
library(nycflights13)
library(tidyverse)
library(scales)
```

the five key dplyr functions:
* Pick observations by their values (filter()).
* Reorder the rows (arrange()).
* Pick variables by their names (select()).
* Create new variables with functions of existing variables (mutate()).
* Collapse many values down to a single summary (summarise()).

x %in% y: select every row where x is one of the values in y
```{r}
(nov_dec <- filter(flights, month %in% c(11, 12)))
```
remembering De Morgan’s law: 
* !(x & y) is the same as !x | !y, and 
* !(x | y) is the same as !x & !y

5.2.4 Exercises
Find all flights that
```{r}
colnames(flights)
# Had an arrival delay of two or more hours
flights %>% filter(arr_delay >= 120)
# Flew to Houston (IAH or HOU)
flights %>% filter(dest %in% c('IAH', 'HOU'))
# Were operated by United, American, or Delta
flights %>% filter(carrier %in% c('UA', 'AA', 'DL'))
# Departed in summer (July, August, and September)
flights %>% filter(month %in% c(7, 8, 9))
# Arrived more than two hours late, but didn’t leave late
flights %>% filter(arr_delay >= 120, dep_delay <= 0)
# Were delayed by at least an hour, but made up over 30 minutes in flight
flights %>% filter(dep_delay >= 60, arr_delay < dep_delay-30)
# Departed between midnight and 6am (inclusive)
flights %>% filter(dep_time <= 600 | dep_time == 2400) # between 24 and 6, include 24 as well!
```
Another useful dplyr filtering helper is between(). What does it do? Can you use it to simplify the code needed to answer the previous challenges?
-- only works for continuous variable
-- for one variable
-- must include "=" sign
-- must within, not falling out!
```{r}
filter(flights, between(month, 7, 9))
```

How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
flights %>% filter(is.na(dep_time))

summary(flights)
```

5.3.1 Exercises
How could you use arrange() to sort all missing values to the start? (Hint: use is.na()).
```{r}
arrange(flights, desc(is.na(dep_time), dep_time))
```
Sort flights to find the most delayed flights. Find the most dep-delayed flights.
```{r}
flights %>% arrange(-dep_delay)
flights %>% arrange(dep_delay)
```
Sort flights to find the fastest (highest speed) flights.
```{r}
flights %>% arrange(-distance/air_time)
```
Which flights travelled the farthest? Which travelled the shortest?
```{r}
flights %>% arrange(distance)
flights %>% arrange(-distance)
```

# Select all columns between year and day (inclusive)
```{r}
select(flights, year:day)
# Select all columns except those from year to day (inclusive)
select(flights, -(year:day))
```

* starts_with("abc"): matches names that begin with “abc”.
* ends_with("xyz"): matches names that end with “xyz”.
* contains("ijk"): matches names that contain “ijk”.
* matches("(.)\\1"): selects variables that match a regular expression. 
*num_range("x", 1:3): matches x1, x2 and x3.

you have a handful of variables you’d like to move to the start of the data frame:
```{r}
select(flights, time_hour, air_time, everything()) # take two columns to the upfront!
```

5.4.1 Exercises
Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.
```{r}
# two fancy methods:
select(flights, starts_with("dep_"), starts_with("arr_"))
select(flights, matches("^(dep|arr)_(time|delay)$"))

```

What happens if you include the name of a variable multiple times in a select() call?
* The select() call ignores the duplication. Any duplicated variables are only included once, in the first location they appear. 
```{r}
flights %>% select(arr_time, arr_time, arr_time)
```
Does the result of running the following code surprise you? How do the select helpers deal with case by default? How can you change that default?
* The default behavior for contains() is to ignore case. 
```{r}
select(flights, contains("TIME"))

select(flights, contains("TIME", ignore.case = FALSE))
```
If you only want to keep the new variables, use transmute():
```{r}
transmute(flights,
  gain = dep_delay - arr_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
```
Modular arithmetic: %/% (integer division) and %% (remainder)
```{r}
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)
```
```{r}
x <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
cumsum(x)  # a sum computed over a rolling window
cummean(x)
```

ranking:
```{r}
y <- c(1, 2, 2, NA, 3, 4)
min_rank(y)
min_rank(desc(y))
row_number(y)
dense_rank(y)
percent_rank(y)
cume_dist(y)
```
5.5.2 Exercises
Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
f1 <- flights %>% mutate(
  dep_time_mins = (dep_time %/% 100 * 60 + dep_time %% 100) %% 1440, 
  # to avoid wrong calculation of 24:00
  sched_dep_time_mins = (sched_dep_time %/% 100 * 60 + sched_dep_time %% 100) %% 1440
) 
```

Compare air_time with arr_time - dep_time. What do you expect to see? What do you see? What do you need to do to fix it?
-- The flight passes midmight
-- Hour zone difference
```{r}
f1 <- f1 %>% 
mutate(arr_dep_cal = (arr_time %/% 100 * 60 + arr_time %% 100) %% 1440 - dep_time_mins)

f1 %>% select(arr_dep_cal, air_time, everything()) %>% filter(arr_dep_cal != air_time)
```

Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?
```{r}
f1 %>% 
  select(sched_dep_time_mins, dep_time_mins, everything()) %>% 
  summarise(dep_diff = dep_delay - dep_time_mins + sched_dep_time_mins, sched_dep_time_mins ) %>% 
  ggplot(aes(x= dep_diff, y= sched_dep_time_mins)) +
  geom_point() 
```
Find the 10 most delayed flights using a ranking function. How do you want to handle ties? Carefully read the documentation for min_rank().
```{r}
flights %>% 
  top_n(10, dep_delay) %>% 
  arrange(-dep_delay)

# option 2
flights %>% 
  arrange(-dep_delay) %>% 
  slice(1:10)
```

What does 1:3 + 1:10 return? Why?
-- When adding two vectors, R recycles the shorter vector’s values to create a vector of the same length as the longer vector. 
```{r}
1:3 + 1:10
```

What trigonometric functions does R provide?
```{r}
x <- seq(-3, 7, by = 1 / 2)
sin(pi * x)
cos(pi * x)
tan(pi * x)
```

It's always a good idea to include either a count (n()), or a count of non-missing values (sum(!is.na(x))). That way you can check that you're not drawing conclusions based on very small amounts of data.
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

delays <- not_cancelled %>% 
  group_by(tailnum) %>% 
  summarise(
    delay = mean(arr_delay, na.rm = TRUE),
    n = n() # the numble of flights which have delays
  )

ggplot(data = delays, mapping = aes(y = delay, x = n)) + 
  geom_point(alpha = 1/11)

delays %>% 
  filter(n > 25) %>% 
  ggplot(mapping = aes(x = n, y = delay)) + 
    geom_point(alpha = 1/10)
```
# Convert to a tibble so it prints nicely
```{r}
(batting <- as_tibble(Lahman::Batting))

# we use subsetting:
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(
    avg_delay1 = mean(arr_delay),
    avg_delay2 = mean(arr_delay[arr_delay > 0]) # the average positive delay
  )
```

You’ve seen n(), which takes no arguments, and returns the size of the current group. 
To count the number of non-missing values, use sum(!is.na(x)). 
To count the number of distinct (unique) values, use n_distinct(x).
```{r}
# Which destinations have the most carriers?
not_cancelled %>% 
  group_by(dest) %>% 
  summarise(carriers = n_distinct(carrier)) %>% 
  arrange(desc(carriers))

# if all you want is a cunt
not_cancelled %>% 
  count(dest)

# You can optionally provide a weight variable. e.g. you could use this to “count” (sum) the total number of miles a plane flew:
not_cancelled %>% 
  count(tailnum, wt = distance)

# you can add conditions within statistical functions:
# How many flights left before 5am? (these usually indicate delayed flights from the previous day)
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(n_early = sum(dep_time < 500))

# What proportion of flights are delayed by more than an hour?
not_cancelled %>% 
  group_by(year, month, day) %>% 
  summarise(hour_prop = mean(arr_delay > 60))
```
Grouping by multiple variables：
```{r}
daily <- group_by(flights, year, month, day)
(per_day   <- summarise(daily, flights = n())) # interesting that you don't have to use group
(per_month <- summarise(per_day, flights = sum(flights)))
(per_year  <- summarise(per_month, flights = sum(flights)))
```

use ungroup for rolled database:
```{r}
daily %>% 
  ungroup() %>%             # no longer grouped by date
  summarise(flights = n())  # all flights
```

5.6.7 Exercises
Come up with another approach that will give you the same output (without using count()).
```{r}
not_cancelled %>% count(dest) 
# answer:
not_cancelled %>%
  group_by(dest) %>% 
  summarise(dest_n = length(dest))
# or 
not_cancelled %>%
  group_by(dest) %>%  
  summarise( n = n()) # treate n = n() as a whole
# or 
not_cancelled %>%
  group_by(dest) %>%
  tally()

not_cancelled %>% count(tailnum, wt = distance) 
# answer:
not_cancelled %>%
  group_by(tailnum) %>% 
  summarise(sum_dis = sum(distance))

# or 
not_cancelled %>%
  group_by(tailnum) %>%
  tally(distance)
```

Which carrier has the worst delays? Challenge: can you disentangle the effects of bad airports vs. bad carriers? Why/why not? (Hint: think about flights %>% group_by(carrier, dest) %>% summarise(n()))
```{r}
flights %>%
  filter(!is.na(arr_delay)) %>%
  # Total delay by carrier within each origin, dest
  group_by(origin, dest, carrier) %>%
  summarise(
    arr_delay = sum(arr_delay),
    flights = n()
  ) %>%
  # Total delay within each origin dest
  group_by(origin, dest) %>%
  mutate(
    arr_delay_total = sum(arr_delay),
    flights_total = sum(flights)
  ) %>%
  # average delay of each carrier - average delay of other carriers
  ungroup() %>%
  mutate(
    arr_delay_others = (arr_delay_total - arr_delay) /
      (flights_total - flights),
    arr_delay_mean = arr_delay / flights,
    arr_delay_diff = arr_delay_mean - arr_delay_others
  ) %>%
  # remove NaN values (when there is only one carrier) this is useful!
  filter(is.finite(arr_delay_diff)) %>%
  # average over all airports it flies to
  group_by(carrier) %>%
  summarise(arr_delay_diff = mean(arr_delay_diff)) %>%
  arrange(desc(arr_delay_diff))
```

What does the sort argument to count() do. When might you use it?
```{r}
flights %>%
  count(dest, sort = TRUE)
```

Which plane (tailnum) has the worst on-time record?
* The question does not define a way to measure on-time record, so I will consider two metrics:
  * proportion of flights not delayed or cancelled (times of delays), and 
  * mean arrival delay. (minutes per delay)

Remove planes that flew at least 20 flights. The choice of 20 was chosen because it round number near the first quantile of the number of flights by plane.
```{r}
quantile(count(flights, tailnum)$n)
```
The plane with the worst on time record that flew at least 20 flights is:
```{r}
flights %>%
  filter(!is.na(tailnum), is.na(arr_time) | !is.na(arr_delay)) %>% # ',' means '&'
  # 'is.na(arr_time) ' means the flight was cancelled!
  mutate(on_time = !is.na(arr_time) & (arr_delay <= 0)) %>%
  group_by(tailnum) %>%
  summarise(on_time = mean(on_time), n = n()) %>%
  filter(n >= 20) %>%
  filter(min_rank(on_time) == 1)
```

* the second way: 
```{r}
flights %>%
  filter(!is.na(arr_delay)) %>%
  group_by(tailnum) %>%
  summarise(arr_delay = mean(arr_delay), n = n()) %>%
  filter(n >= 20) %>%
  filter(min_rank(desc(arr_delay)) == 1)
```

What time of day should you fly if you want to avoid delays as much as possible?
* This is intuitive as delays will affect later flights. Morning flights have fewer (if any) previous flights that can delay them.
```{r}
flights %>% 
  group_by(hour) %>% 
  summarise(arr_delay_m = mean(arr_delay, na.rm = TRUE)) %>% 
  arrange(arr_delay_m)
```

```{r}
flights
```

For each destination, compute the total minutes of delay. For each flight, compute the proportion of the total delay for its destination.
```{r}
flights %>% 
  filter(arr_delay > 0) %>% 
  group_by(dest) %>% 
  summarise(delay_sum = sum(arr_delay)) %>% 
  arrange(delay_sum)

flights %>%
  filter(arr_delay > 0) %>%
  group_by(flight, dest) %>%
  summarise(arr_delay = sum(arr_delay)) %>% 
  # if we use summarise here, 'dest' will be overwritten!
  mutate(arr_delay_prop = arr_delay / sum(arr_delay)) %>% 
  arrange(flight, desc(arr_delay_prop)) 
```












